---
title: "Shab-Analyse"
author: "Claudio Lutz"
date: "2024-07-28"
output:
  html_document: default
  pdf_document: default
---


## Einführung

## HR01

Dieser Code wird für die Registrierung neuer Unternehmen im Handelsregister verwendet. Wenn ein neues Unternehmen gegründet und registriert wird, erfolgt die Veröffentlichung unter HR01. Dies umfasst Details wie den Firmennamen, den Sitz, den Zweck und die Namen der Verwaltungsratsmitglieder oder Geschäftsführer.

## HR03

Dieser Code bezieht sich auf die Löschung eines Unternehmens aus dem Handelsregister. Dies geschieht, wenn ein Unternehmen aufgelöst, liquidiert oder anderweitig nicht mehr als registrierte Einheit existiert. Die Löschung muss beantragt werden, wenn beispielsweise ein Einzelunternehmen nicht mehr existiert oder an eine andere Person übergeht.

Weitere Informationen zu den Eintragungspflichten und -verfahren befinden sich auf folgender Seite:

- [Handelsregister: Rechte und Pflichten für KMU](https://www.kmu.admin.ch/kmu/de/home/praktisches-wissen/kmu-gruenden/firmengruendung/handelsregister.html)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=10)
```

```{r installiere_libraries, echo=TRUE, results='hide', message=FALSE, warning=FALSE}
if (!require(tidyr)) install.packages("tidyr")
if (!require(httr)) install.packages("httr")
if (!require(XML)) install.packages("XML")
if (!require(dplyr)) install.packages("dplyr")
if (!require(ggplot2)) install.packages("ggplot2")
if (!require(gridExtra)) install.packages("gridExtra")
if (!require(patchwork)) install.packages("patchwork")
if (!require(skimr)) install.packages("skimr")
if (!require(broom)) install.packages("broom")
if (!require(forecast)) install.packages("forecast")
if (!require(scales)) install.packages("scales")
if (!require(tidyr)) install.packages("tidyr")
if (!require(tidytext)) install.packages("tidytext")
```


```{r lade_libraries, echo=TRUE, results='hide', message=FALSE, warning=FALSE}
library(httr)
library(XML)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(lubridate)
library(patchwork)
library(skimr)
library(broom)
library(forecast)
library(scales)
library(tidyr)
library(tidytext)
source("get_shab_data.R")

calc_confidence_interval <- function(proportion, total, alpha = 0.05) {
  if (is.na(total) || total == 0 || is.na(proportion) || proportion < 0 || proportion > 1) {
    return(c(NA_real_, NA_real_))
  }
  # If proportion is 0 or 1, std_error will be 0. qnorm(..., sd = 0) correctly returns the mean.
  std_error <- sqrt((proportion * (1 - proportion)) / total)
  if (is.na(std_error)) { # Should be covered by initial checks, but as a safeguard
      return(c(NA_real_, NA_real_))
  }
  lower_bound <- qnorm(alpha / 2, mean = proportion, sd = std_error)
  upper_bound <- qnorm(1 - alpha / 2, mean = proportion, sd = std_error)
  return(c(lower_bound, upper_bound))
}
```


```{r lade_daten_falls_nötig, warning=FALSE}
# Scrape alle relevanten Shab-Daten über einen Zeitraum. Es werden nur die Daten heruntergeladen welche noch nicht lokal gespeichert sind.
from_date <- as.Date("2018-03-18")
to_date <- as.Date("2024-10-20")
shab_data <- Get_Shab_DF_from_range(from_date, to_date)

skim(shab_data)
```
```{r filter_dataset}
first_full_month <- floor_date(min(shab_data$date), "month")
last_full_month <- floor_date(max(shab_data$date), "month") - months(1)

first_data_date <- min(shab_data$date)
if (day(first_data_date) != 1) {
  first_full_month <- floor_date(first_data_date + months(1), "month")
}

data <- shab_data %>%
  filter(date >= first_full_month & date <= last_full_month)
```



```{r}
# Alle benötigten Datumsspalten
data$date <- as.Date(data$date)
data$month <- format(data$date, "%m")
data$quarter_label <- paste0(year(data$date), "_Q", quarter(data$date))
data$year <- format(data$date, "%Y")
data$quarter_year <- floor_date(data$date, "quarter")
data$year_month <- format(data$date, "%Y-%m")

# Date Varbiablen
current_year <- format(Sys.Date(), "%Y")
covid_start <- as.Date("2020-03-01")
covid_end <- as.Date("2021-06-01")
covid_middle <- as.Date("2020-07-01") 

```

# Zuwachs an Firmen
Aufgrund der höheren Anzahl Eintragungen gegenüber Löschungen nimmt die Anzahl eingetragenen Firmen zu.

```{r Zunahme_an_Firmen}

hr01_data <- subset(data, subrubric == "HR01")
hr03_data <- subset(data, subrubric == "HR03")

hr01_counts <- aggregate(id ~ year_month, data = hr01_data, FUN = length)
hr03_counts <- aggregate(id ~ year_month, data = hr03_data, FUN = length)

# Rename columns for merging
colnames(hr01_counts) <- c("year_month", "HR01_count")
colnames(hr03_counts) <- c("year_month", "HR03_count")

# Merge the data on year_month
monthly_counts <- merge(hr01_counts, hr03_counts, by = "year_month", all = TRUE)
monthly_counts[is.na(monthly_counts)] <- 0

# Calculate the difference
monthly_counts$difference <- monthly_counts$HR01_count - monthly_counts$HR03_count

# Calculate the net change for each month
monthly_counts$net_change <- monthly_counts$HR01_count - monthly_counts$HR03_count

# Calculate the cumulative sum of the net changes
monthly_counts$cumulative_total <- cumsum(monthly_counts$net_change)

# Create the cumulative total plot
plot_cumulative <- ggplot(monthly_counts, aes(x = as.Date(paste0(year_month, "-01")))) +
  geom_line(aes(y = cumulative_total, color = "Cumulative Total")) +
  labs(title = "Cumulatives Total auf Zeit",
       x = "Monat",
       y = "Cumulatives Total",
       color = "Legend") +
  theme_minimal() +
  theme(legend.position = "none")

# Create the log scale plot without the legend
plot_log_scale <- ggplot(monthly_counts %>% dplyr::filter(cumulative_total > 0), aes(x = as.Date(paste0(year_month, "-01")))) +
  geom_line(aes(y = cumulative_total, color = "Cumulative Total")) +
  scale_y_log10() +
  labs(title = "Cumulatives Total auf Zeit (Log Scale)",
       x = "Monat",
       y = "Cumulatives Total (Log Scale)") +
  theme_minimal() +
  theme(legend.position = "none")

# Combine the two plots using patchwork
combined_plot <- plot_cumulative + plot_log_scale + plot_layout(ncol = 2)

# Print the combined plot
print(combined_plot)
```

```{r Nettozuwachs_pro_Monat}
agg_data <- data %>%
  group_by(year_month, subrubric) %>%
  summarise(count = n(), .groups = "drop")

# Ensure all months have both subrubrics (HR01 and HR03)
all_months <- unique(agg_data$year_month)
all_subrubrics <- c("HR01", "HR03")
complete_data <- expand.grid(year_month = all_months, subrubric = all_subrubrics) %>%
  left_join(agg_data, by = c("year_month", "subrubric")) %>%
  mutate(count = ifelse(is.na(count), 0, count))

# Generate the sequence of months that are the start of each quarter
start_of_quarters <- unique(complete_data$year_month[month(as.Date(paste0(complete_data$year_month, "-01"))) %% 3 == 1])

# Calculate the difference between HR01 and HR03 as Netto Zuwachs
difference_data <- complete_data %>%
  spread(key = subrubric, value = count) %>%
  mutate(NettoZuwachs = HR01 - abs(HR03)) %>%
  select(year_month, NettoZuwachs)

# Merge the difference data back with the complete_data
final_data <- complete_data %>%
  left_join(difference_data, by = "year_month") %>%
    mutate(quarter_label = ifelse(year_month %in% start_of_quarters, paste0(substr(year_month, 1, 4), "_Q", quarter(as.Date(paste0(year_month, "-01")))), ""),
         year_month = factor(year_month, levels = unique(year_month)))  # Convert month to a factor

# Transform counts: HR03 to negative values
final_data <- final_data %>%
  mutate(count = ifelse(subrubric == "HR03", -count, count))

# Plot HR01 and HR03 with stacking
p <- ggplot(final_data, aes(x = year_month)) +
  geom_col(aes(y = count, fill = subrubric), position = "stack") +
  geom_hline(yintercept = 0, color = "black") +
  scale_y_continuous(labels = abs) +
  scale_x_discrete(labels = final_data$quarter_label) +
  scale_fill_manual(
    values = c("HR01" = "Darkgreen", "HR03" = "#FF474C", "Netto Zuwachs" = "gray50"),
    labels = c("HR01" = "Neueintragung", "HR03" = "Löschung", "Netto Zuwachs" = "Netto Zuwachs")
    ) +
  labs(
    title = "Anzahl Neueintragungen, Anzahl Löschungen und Nettozuwachs",
    x = "Monat",
    y = "Anzahl",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_line(color = "grey80"),
    panel.grid.minor.y = element_blank()
  )

# Add Netto Zuwachs as a separate bar without stacking
p + geom_col(data = final_data, aes(x = year_month, y = NettoZuwachs, fill = "Netto Zuwachs"), width = 0.3, color = "black")
```

```{r Nettozuwachs_nach_Kanton}
# Group the data by Kanton and subrubric, then aggregate
agg_data_kanton <- data %>%
  group_by(kanton, subrubric) %>%
  summarise(count = n(), .groups = "drop")

# Ensure all Kantons have both subrubrics (HR01 and HR03)
all_kantons <- unique(agg_data_kanton$kanton)
all_subrubrics <- c("HR01", "HR03")
complete_data_kanton <- expand.grid(kanton = all_kantons, subrubric = all_subrubrics) %>%
  left_join(agg_data_kanton, by = c("kanton", "subrubric")) %>%
  mutate(count = ifelse(is.na(count), 0, count))

# Calculate the difference between HR01 and HR03 as Netto Zuwachs
difference_data_kanton <- complete_data_kanton %>%
  spread(key = subrubric, value = count) %>%
  mutate(NettoZuwachs = HR01 - abs(HR03)) %>%
  select(kanton, NettoZuwachs)

# Merge the difference data back with the complete_data
final_data_kanton <- complete_data_kanton %>%
  left_join(difference_data_kanton, by = "kanton") %>%
  arrange(NettoZuwachs, kanton) %>%  # Break ties by alphabetical order of Kanton
  mutate(kanton = factor(kanton, levels = unique(kanton)))  # Convert kanton to a factor with ordered levels

# Transform counts: HR03 to negative values
final_data_kanton <- final_data_kanton %>%
  mutate(count = ifelse(subrubric == "HR03", -count, count))

# Plot HR01 and HR03 with stacking
p <- ggplot(final_data_kanton, aes(x = kanton)) +
  geom_col(aes(y = count, fill = subrubric), position = "stack") +
  geom_hline(yintercept = 0, color = "black") +
  scale_y_continuous(labels = abs) +
  scale_fill_manual(
    values = c("HR01" = "Darkgreen", "HR03" = "#FF474C", "Netto Zuwachs" = "gray50"),
    labels = c("HR01" = "Neueintragung", "HR03" = "Löschung", "Netto Zuwachs" = "Netto Zuwachs")
    ) +
  labs(
    title = "Kantonale Zählung von Neueintragungen und Löschungen, sortiert nach Netto Zuwachs",
    x = "Kanton",
    y = "Number of Records",
    fill = "Subrubric"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_line(color = "grey80"),
    panel.grid.minor.y = element_blank()
  )

# Add Netto Zuwachs as a separate bar without stacking
p + geom_col(data = final_data_kanton, aes(x = kanton, y = NettoZuwachs, fill = "Netto Zuwachs"), width = 0.3, color = "black")
```
```{r Prozentuale_Verteilung}
# Calculate relative contributions of HR01 and HR03
relative_contribution <- complete_data_kanton %>%
  group_by(kanton, subrubric) %>%
  summarise(total_count = sum(count), .groups = 'drop') %>%
  group_by(kanton) %>%
  mutate(percentage = total_count / sum(total_count) * 100)

# Order Kantons by the percentage of HR01
ordered_kantons <- relative_contribution %>%
  filter(subrubric == "HR01") %>%
  arrange(desc(percentage)) %>%
  pull(kanton)

relative_contribution <- relative_contribution %>%
  mutate(kanton = factor(kanton, levels = ordered_kantons))

ggplot(relative_contribution, aes(x = kanton, y = percentage, fill = subrubric)) +
  geom_col(color = "black") +  
  
  # Labels for HR01 at the bottom of the bars
  geom_text(aes(label = ifelse(percentage > 5, paste0(round(percentage, 1), "%"), "")),
            position = position_stack(vjust = 0.5),
            size = 3,
            color = "black") +

  labs(
    title = "Prozentuale Verteilung von Neueintragung und Löschungen nach Kanton",
    x = "Kanton",
    y = "Prozent",
    fill = "Subrubric"
  ) +
  scale_fill_manual(
    values = c("HR01" = "Darkgreen", "HR03" = "#FF474C"),
    labels = c("HR01" = "Neueintragung", "HR03" = "Löschung")
    ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )


```

```{r,fig.width=10, fig.height=10, echo=TRUE}
# Aggregate the data by year, kanton, and subrubric, then calculate percentages
agg_data <- data %>%
  group_by(year, kanton, subrubric) %>%
  summarise(total_count = n(), .groups = 'drop') %>%
  group_by(year, kanton) %>%
  mutate(percentage = total_count / sum(total_count) * 100)

# Create the overview plot with data over all years
overview_plot <- ggplot(agg_data, aes(x = kanton, y = percentage, fill = subrubric)) +
  geom_bar(stat = "identity", width = 0.8) +
  labs(
    title = "Anzahl Gründungen und Löschungen über die ganze Periode pro Kanton",
    fill = "Subrubric"
  ) +
  scale_fill_manual(
    values = c("HR01" = "Darkgreen", "HR03" = "#FF474C"),
    labels = c("HR01" = "Neueintragung", "HR03" = "Löschung")
    ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_blank(),  # Remove x-axis title
    axis.title.y = element_blank(),  # Remove y-axis title
    legend.position = "top",  # Legend at the top
    legend.direction = "horizontal"
  )

# Create an empty list to store the plots
plots <- list()

# Loop through each year
for (yr in unique(agg_data$year)) {
  
  # Filter the data for the current year
  year_data <- agg_data %>% filter(year == yr)
  
  # Determine the order of Kantons based on HR01 percentage within the current year
  hr01_order <- year_data %>%
    filter(subrubric == "HR01") %>%
    arrange(desc(percentage)) %>%
    pull(kanton)
  
  # Apply the ordering to the year's data
  year_data <- year_data %>%
    mutate(kanton = factor(kanton, levels = hr01_order))
  
  # Create the plot for the current year without the legend
  p <- ggplot(year_data, aes(x = kanton, y = percentage, fill = subrubric)) +
    geom_bar(stat = "identity", width = 0.8) +
    labs(
      title = paste('Anzahl Gründungen und Löschungen ', yr)
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.text.y = element_text(size = 10),
      strip.text = element_text(size = 12),
      axis.title.x = element_blank(),  # Remove x-axis title
      axis.title.y = element_blank(),  # Remove y-axis title
      legend.position = "none"  # Remove legend from individual plots
    ) +
  
  scale_fill_manual(
    values = c("HR01" = "Darkgreen", "HR03" = "#FF474C"),
    labels = c("HR01" = "Neueintragung", "HR03" = "Löschung")
    ) +
    coord_cartesian(ylim = c(30, 55))  # Adjust the y-axis limits with coord_cartesian
  
  # Store the plot in the list
  plots[[yr]] <- p
}

# Combine the overview plot with the individual year plots using patchwork
final_plot <- (overview_plot / wrap_plots(plots, ncol = 2)) + 
  plot_layout(heights = c(2, 10))

# Display the combined plot grid
final_plot


```

```{r warning=FALSE}
# Remove scaling part if you want to display the raw difference
monthly_counts$difference <- monthly_counts$HR01_count - monthly_counts$HR03_count

# Create the plot with the orange background for the COVID period and a "Covid" annotation
ggplot(monthly_counts, aes(x = as.Date(paste0(year_month, "-01")))) +
  geom_rect(
    aes(xmin = covid_start, xmax = covid_end, ymin = -Inf, ymax = Inf),
    fill = "orange", alpha = 0.01
  ) +  
  geom_line(aes(y = HR01_count, color = "HR01 Count"), size = 1.2) +  # Line for Neueintragung
  geom_line(aes(y = HR03_count, color = "HR03 Count"), size = 1.2) +  # Line for Löschung
  geom_line(aes(y = difference, color = "Difference"), size = 1.2) +  # Line for raw difference (HR01 - HR03)
  scale_y_continuous(name = "Count") +  # Single y-axis for all lines
  scale_color_manual(
    values = c("HR01 Count" = "Darkgreen", "HR03 Count" = "#FF474C", "Difference" = "gray50"),
    labels = c("HR01 Count" = "Neueintragung", "HR03 Count" = "Löschung", "Difference" = "Unterschied")
  ) +
  labs(
    title = "Monatliche Eintragungen, Löschungen und Unterschied",
    x = "Monat",
    color = NULL  
  ) +
  annotate("text", x = covid_middle, y = Inf, label = "Covid", vjust = 2, size = 5, color = "black") + 
  theme_minimal() +
  theme(legend.position = "bottom")  

```
```{r}

data_summary <- data %>%
  group_by(quarter_year, kanton, subrubric) %>%
  summarise(entries = n(), .groups = "drop")

ggplot(data_summary, aes(x = quarter_year, y = entries, color = subrubric)) +
  geom_line() +
  geom_rect(
    aes(xmin = covid_start, xmax = covid_end, ymin = -Inf, ymax = Inf),
    fill = "orange", alpha = 0.01, color = NA 
  ) +  
  labs(title = "Anzahl Einträge und Löschunugen pro Kanton", x = NULL, y = "Number of Entries") +
  facet_wrap(~ kanton, scales = "free_y") +
    scale_color_manual(
    values = c("HR01" = "Darkgreen", "HR03" = "#FF474C"),
    labels = c("HR01" = "Neueintragung", "HR03" = "Löschung")
  ) +

  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(size = 14),
        axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        strip.text = element_text(size = 8),
        legend.text = element_text(size = 8),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r}
monthly_counts_prop <- data %>%
  group_by(year_month, subrubric) %>%
  summarise(count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = subrubric, values_from = count, values_fill = 0)

monthly_counts_prop <- monthly_counts_prop %>%
  mutate(total = HR01 + HR03,
         proportion = HR01 / total)

alpha <- 0.05  # 95% confidence level

# calc_confidence_interval is now defined in lade_libraries chunk

monthly_counts_prop <- monthly_counts_prop %>%
  rowwise() %>%
  mutate(
    lower_bound = calc_confidence_interval(proportion, total)[1],
    upper_bound = calc_confidence_interval(proportion, total)[2]
  )

monthly_counts_prop$year_month_date <- as.Date(paste0(monthly_counts_prop$year_month, "-01"), format = "%Y-%m-%d")

ggplot(monthly_counts_prop, aes(x = year_month_date, y = proportion)) +
  geom_rect(
    xmin = covid_start, xmax = covid_end, ymin = -Inf, ymax = Inf,
    fill = "orange", alpha = 0.01
  ) +  
  geom_line(color = "blue", linewidth = 1) +  
  geom_ribbon(aes(ymin = lower_bound, ymax = upper_bound), fill = "lightblue", alpha = 0.3) +  
  labs(title = "Anteil der Neueintragungen im Zeitverlauf mit 95%-Konfidenzintervall",
       x = "Monat", y = "Anteil") +
  annotate("text", x = covid_middle, y = Inf, label = "Covid", vjust = 2, size = 5, color = "black") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +  
  scale_x_date(date_labels = "%Y-%m", date_breaks = "3 months") 
```
Während der COVID-19-Pandemie gab einen Stopp von Löschungen (HR03), was bedeutet, dass weniger Unternehmen aus dem Handelsregister gelöscht wurden. Da die Löschungen nicht stattfanden, blieb die Anzahl der HR01-Neuregistrierungen im Verhältnis zur Gesamtheit der Einträge (HR01 + HR03) höher. Dies könnte ein Grund dafür sein, dass die Linie für den Anteil der Neuregistrierungen in dieser Zeit nach oben ging.

Da die HR01-Anmeldungen stattfanden, die HR03-Löschungen jedoch gestoppt wurden, führte dies zu einem künstlichen Anstieg des Anteils von HR01 in der Statistik. Nach Ende des Stopps von Löschungen kehrte das Verhältnis wieder zu einem normaleren Muster zurück.
```{r}

# Step 2: Summarize HR01 and HR03 counts by canton and quarter-year
data_summary <- data %>%
  group_by(quarter_year, kanton, subrubric) %>%
  summarise(entries = n(), .groups = "drop") %>%
  pivot_wider(names_from = subrubric, values_from = entries, values_fill = 0) %>%
  mutate(total = HR01 + HR03,
         proportion = HR01 / total)

# Step 3: Define the function to calculate the confidence interval for proportions
# calc_confidence_interval is now defined in lade_libraries chunk

# Step 4: Apply the confidence interval function for each canton/quarter combination
data_summary <- data_summary %>%
  rowwise() %>%
  mutate(
    lower_bound = calc_confidence_interval(proportion, total)[1],
    upper_bound = calc_confidence_interval(proportion, total)[2]
  ) %>%
  ungroup()

# Step 5: Create the faceted plot with only proportion and confidence interval
ggplot(data_summary, aes(x = quarter_year)) +
  # Add Covid period shading
  geom_rect(
    aes(xmin = covid_start, xmax = covid_end, ymin = -Inf, ymax = Inf),
    fill = "orange", alpha = 0.01, color = NA 
  ) +
  # Line for proportion of HR01
  geom_line(aes(y = proportion), color = "blue", linetype = "solid") +
  # Confidence intervals as ribbon
  geom_ribbon(aes(ymin = lower_bound, ymax = upper_bound), fill = "lightblue", alpha = 0.3) +
  # Set y-axis limits to match the range of proportions
  scale_y_continuous(name = "Proportion of HR01") +
  # Facet by canton
  facet_wrap(~ kanton, scales = "free_y") +
  # Customize plot
  labs(title = "Proportion of HR01 (New Registrations) Over Time by Kanton",
       x = "Quarter-Year", y = "Proportion of HR01") +
  theme_minimal() +
  theme(legend.position = "none",
        plot.title = element_text(size = 14),
        axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        strip.text = element_text(size = 8),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```


```{r warning=FALSE}

# Count occurrences by date
hr01_counts_daily <- hr01_data %>%
  group_by(date) %>%
  summarise(HR01_count = n())

hr03_counts_daily <- hr03_data %>%
  group_by(date) %>%
  summarise(HR03_count = n())

# Merge the data on date
daily_counts <- merge(hr01_counts_daily, hr03_counts_daily, by = "date", all = TRUE)
daily_counts[is.na(daily_counts)] <- 0

# Calculate the difference
daily_counts$difference <- daily_counts$HR01_count - daily_counts$HR03_count

# Perform linear regression on HR01_count and HR03_count
lm_model_daily <- lm(HR01_count ~ HR03_count, data = daily_counts)

# Summarize the model
summary(lm_model_daily)

# Extract tidy results with confidence intervals and p-values
tidy_results_daily <- tidy(lm_model_daily, conf.int = TRUE)
tidy_results_daily

# Plot regression line with confidence interval
ggplot(daily_counts, aes(x = HR03_count, y = HR01_count, colour = factor(wday(date)))) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "Linear Regression of HR01 Count on HR03 Count (Daily Data)",
       x = "HR03 Count",
       y = "HR01 Count") +
  theme_minimal()
```

```{r}
ggplot(daily_counts, aes(x = HR03_count, y = HR01_count)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "Linear Regression of HR01 Count on HR03 Count (Daily Data)",
       x = "HR03 Count",
       y = "HR01 Count") +
  theme_minimal()
```



```{r}
count_per_date <- data %>%
  group_by(date, subrubric) %>%
  summarise(count = n())

hr03_data <- count_per_date %>% filter(subrubric == "HR03")
hr01_data <- count_per_date %>% filter(subrubric == "HR01")

fit_hr03 <- lm(count ~ date, data = hr03_data)
fit_hr01 <- lm(count ~ date, data = hr01_data)

intercept_hr03 <- coef(fit_hr03)[1]
slope_hr03 <- coef(fit_hr03)[2]

intercept_hr01 <- coef(fit_hr01)[1]
slope_hr01 <- coef(fit_hr01)[2]

# Plot both subrubrics in the same plot with thicker regression lines
ggplot(count_per_date, aes(x = date, y = count, color = subrubric)) +
  geom_point() +
  geom_abline(intercept = intercept_hr03, slope = slope_hr03, color = '#FF474C', size = 1.2, linetype = "solid") +
  geom_abline(intercept = intercept_hr01, slope = slope_hr01, color = "Darkgreen", size = 1.2, linetype = "solid") +
  labs(title = "Regression of Subrubric HR03 and HR01 Counts Over Time",
       x = "Date",
       y = "Count",
       color = "Subrubric") +
    scale_color_manual(
    values = c("HR01" = "Darkgreen", "HR03" = "#FF474C"),
    labels = c("HR01" = "Neueintragung", "HR03" = "Löschung")
  ) +
  theme_minimal()

```


```{r warning=FALSE}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(patchwork)

hr03_data <- subset(data, subrubric == "HR03" & as.numeric(year) >= 2020)
hr03_counts <- hr03_data %>%
  group_by(year, month) %>%
  summarise(count = n(), .groups = 'drop')

hr01_data <- subset(data, subrubric == "HR01" & as.numeric(year) >= 2020)
hr01_counts <- hr01_data %>%
  group_by(year, month) %>%
  summarise(count = n(), .groups = 'drop')

# Define line sizes
line_size_current <- 1
line_size_other <- 0.5

# Create the HR03 plot with adjusted line sizes and gradient color for years, excluding 2018
plot_hr03 <- ggplot(hr03_counts, aes(x = month, y = count, group = year, color = as.numeric(year))) +
  geom_line(aes(size = ifelse(year == current_year, line_size_current, line_size_other))) +
  labs(title = "Monthly HR03 Counts by Year",
       x = "Month",
       y = "Count",
       color = "Year") +
  scale_x_discrete(limits = sprintf("%02d", 1:12)) +
  theme_minimal() +
  scale_size_identity() +  # Ensure size is used as is
  scale_color_gradient(low = "blue", high = "red") +  # Gradient from blue to red
  guides(size = "none")

# Create the HR01 plot with adjusted line sizes and gradient color for years, excluding 2018
plot_hr01 <- ggplot(hr01_counts, aes(x = month, y = count, group = year, color = as.numeric(year))) +
  geom_line(aes(size = ifelse(year == current_year, line_size_current, line_size_other))) +
  labs(title = "Monthly HR01 Counts by Year",
       x = "Month",
       y = "Count",
       color = "Year") +
  scale_x_discrete(limits = sprintf("%02d", 1:12)) +
  theme_minimal() +
  scale_size_identity() +  # Ensure size is used as is
  scale_color_gradient(low = "blue", high = "red") +  # Gradient from blue to red
  guides(size = "none")

# Combine the plots using patchwork
combined_plot <- plot_hr03 + plot_hr01 + plot_layout(ncol = 1, heights = c(1, 1))

# Print the combined plot
print(combined_plot)

```


